### 2020-10-14 latex/acrobot.tex
Added the section on previous constraints in Acrobot chapter

\section{Previous Constraint Approaches}
% TODO: Give Xingbo's intuition, abstract away to qa = sin(theta) constraint
% based on VLP but show it doesn't work well in our framework
% TODO: Describe Xingbo's results and observe that his results were similar to a VNHC
% except they used VHC tools. We will modify his approach to use VNHCs and prove
% rigorously that we can stabilize any energy level set on the acrobot.

>>>>

\section{Previous Constraint Approaches}
% TODO: Give Xingbo's intuition, abstract away to qa = sin(theta) constraint
% based on VLP but show it doesn't work well in our framework
% TODO: Describe Xingbo's results and observe that his results were similar to a VNHC
% except they used VHC tools. We will modify his approach to use VNHCs and prove
% rigorously that we can stabilize any energy level set on the acrobot.
As we saw at the beginning of this chapter, there are some existing approaches
to generating giant motion for the acrobot.
We will examine a few of these approaches and examine whether they are viable
candidates on which to base a VNHC, akin to how we designed the VLP constraint
in Chapter \ref{ch:vlp}.

An instinctive approach to controlling the acrobot is to model it as a
variable-length pendulum as in Figure \ref{fig:acrobot-ecm}, 
since the length of its equivalent center of mass (ECM) changes with the leg motion. 
For instance, \citet{swingup_giant_acrobot} design a desired trajectory for the
ECM, then determine which leg angles \(q_a(t)\) are required to generate that
trajectory.

\begin{figure}
    \centering
    \includestandalone[width=0.5\textwidth]{images/acrobot_ecm}
    \caption{A simple acrobot modelled as a VLP with equivalent center of mass \(2m\). 
        The length of the VLP changes according to \(q_a\).}
    \label{fig:acrobot-ecm}
\end{figure}

Unfortunately, the VLP is not a true representation of the acrobot.
The effective length of the ECM is 
\[
    l_e(q_a) := l\sqrt{\frac{5}{4} + cos(q_a)}
    ,
\]
and its effective angle is
\[
    q_e := \arctan_2(s_u + \frac{1}{2}s_{ua}, -c_u - \frac{1}{2}c_{ua})
    .
\]
There are two things of note here. 
First, Figure \ref{fig:acrobot-vlp-symmetry} shows there are two configurations
of the acrobot which give the same effective angle and length.
This means the acrobot and the VLP are not equivalent representations;
designing a VNHC that injects energy using the ECM may not produce human-like
leg motion on the acrobot.
Second, the torque input \(\tau\) applied to \(q_a\) affects both
\(l_e\) and \(q_e\). 
In the VLP model from Chapter \ref{ch:vlp}, the control input only
affects the dynamics of the length variable.
If we wanted to design a VNHC to provably inject energy into the acrobot, we
would need to fully redesign the VLP constraint with a model where the control
input has a direct effect on the angle.

\begin{figure}
    \centering
    % TODO: Generate a figure with the ECM at one position, and two mirrored
    % acrobots (dashed) around it to show how the VLP and acrobot are not
    % equivalent.
%    \includestandalone[width=0.5\textwidth]{}
    \caption{The equivalent center of mass of the acrobot generally has two configurations
        which correspond to the same effective length and angle. These
        configurations are symmetric about the line connecting the pivot to the
        ECM.}
    \label{fig:acrobot-vlp-symmetry}
\end{figure}

Since the VLP representation of the acrobot requires redesigning a VLP
controller, and the resulting motion may not even be realistic giant motion,
this model is clearly ineffective for our purposes.

We turn to the thesis of \citet{xingbo_thesis}, who designs a VHC to enforce a
so-called ``tap" motion, with the purpose of injecting energy into the acrobot. 
First, he defines a compensator variable \(s\) which tracks \(\dot{q}_u\), so
that he can use the theory of VHCs with the extended configuration 
\((q_u,q_a,s)\).
He then finds \(h_1, h_2 \in \R_{>0}\) to define the
normalized radius \(\rho\) and normalized angle \(\xi\) in the
\((q_u, s)\)-plane.
These normalized variables are given by
\begin{align*}
    \rho &:= \sqrt{h_1 q_u^2 + h_2 s^2}
    , \\
    \xi &:= \arctan_2(h_2 s, h_1 q_u)
    . 
\end{align*}
He then sets the VHC to be \(h(q) = q_a - f_\text{rad}(\rho)f_\text{ang}(\xi)\)
with the control parameters \(\bar{q}_u\) and \(\rho_0\), where
\begin{align*}
    f_\text{rad}(\rho) &:= \tanh^2(\rho/\rho_0)
    , \\
    f_\text{ang}(\xi) &:= 
    \begin{cases}
        0 & -\pi < \xi \leq 0 \\
        \bar{q}_u \exp\left(1 - \frac{1}{1-(\frac{4\xi}{\pi} - 1)^2}\right) 
          & 0 < \xi \leq \frac{\pi}{2} \\
        0 & \frac{\pi}{2} < \xi \leq \pi
        .
    \end{cases}
\end{align*}

While his VHC shows promising experimental results, \citeauthor{xingbo_thesis}
does not provide an analytical proof that the acrobot gains energy.
His lack of analysis is tied to the fact that the constrained
(Lagrangian) dynamics are incredibly complicated.
In fact, it is even challenging to show that the constraint is regular.
While we could very easily convert his VHC into a VNHC by replacing \(s\) with
\(p_u\), we would run into the same problem. 
Since we want our constraint to \textit{provably} inject energy, we choose to
forgo this type of constraint.
